Efficient Coalition Formation \\ for Web Services

### 2013-06-15 papers/coalition-journal-extension/coalition_journal.tex
Changes

We discuessed $core$ as one the preeminent solution concepts in cooperative games. Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group. However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept opening room for agents to cooperate and stay in the community and increasing the community stability. The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent point of view. It claims agents for any reason will be not willing to deviate to gain less that $\epsilon$ amount of profit. However, in our case, the community master is willing to keep web services in communities too. There are several reasons for this, one is there is always possibility that agents may leave the community or they may under perform from the values they initially performing with. According to the web service community's valuation function \ref{eq:valuation} and as mentioned in examples 1, 2 and 3,

>>>>

We discuessed $core$ as one the preminent solution concepts in cooperative games. Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group. However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal ammount of $\epsilon$ by deviating. The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent's point of view. It claims agents for any reason will be not willing to deviate to gain less than $\epsilon$ amount of profit. However, in our case, the community master is willing to keep web services in communities too. There are several reasons for this, one reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with. To this end, our communities will reward and valuate web services in the community
